Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-20 article_review/Manuscript.tex
More changes for the review

\newcommand{\comment}[1]{{\color{cyan} (Toni) #1 }}
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

{\color{purple} (Lolo) 
\begin{definition}
\label{rep.designs}
Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1]^{d}$. Assume that the points $\vx_i$ (resp. $\vx'_i$) are all coordinate-wise different; that is $\forall (i_1,i_2) \in \{0,,n-1\}^2$, such that $i_1 \neq i_2$: $$x_{i_1,j} \neq x_{i_2,j}, \qquad \forall j=1,\dots,d .$$
Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. ${\mathcal{P}'}^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if for any $u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1]^a$. We define by $\pi_u$ the permutation that rearranges the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$.
\end{definition}

\begin{remark}
In the following, the two replicated designs $\mathcal{P}$, $\mathcal{P}'$ are constructed to avoid the degenerate case $\forall i \ \vx_i = \vx'_i$. 
\end{remark}}

@@

\comment{We assumed that evaluating our model is expensive. Thus, we will focus our cost study on the number of function evaluations needed to estimate the indices. The function evaluations used to estimate the indices are the same as the ones used to compute the discrete Walsh coefficients. The only computation cost that could be expensive is the fast transform algorithm. However, on a regular laptop computing the discrete coefficients of $2^{20}$ points takes around $0.5$ seconds while evaluating these points at an average evaluation time of $1$ microsecond, takes a total of around $1$ second.}

@@

Then, one must construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ at Step $5$ according to the multiplicative approach detailed in \cite{GJAHMP}. {\color{purple} (Lolo) This approach iteratively constructs a $2d$-dimensional Sobol' sequence then assigns its first $d$ coordinates to $\mathcal{P}_{m}$ and its last $d$ coordinates to $\mathcal{P}'_{m}$. The $2d$-dimension Sobol' sequence is generated based on the directional numbers found in \cite{Kuo}. These directional numbers insure better two-dimensional projections of the resulting Sobol' sequence. In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling scheme \cite{HonHic00a,Owe95}.......}

@@

We illustrate our sequential estimation procedure with two classical test functions and one real example. In each case, Sobol' indices are estimated with the following three variants:
\begin{itemize}
\item[$\bullet$] Variant $A.a$ as Variant $A$ without using ``Correlation 2''. 
\item[$\bullet$] Variant $A.b$ as Variant $A$ using ``Correlation 2''.
\item[$\bullet$] Variant $B$.
\end{itemize}
The threshold to decide whether or not a first-order index is small is set to $0.1$.

@@

%\comment{As a real case example, we will study the wing weight function:
%\begin{align*}
%f(\vx)=0.036 x_1^{0.758} & x_2^{0.0035} \left(\frac{x_3}{\cos(x_4)^2}\right)^{0.6} x_5^{0.006} x_6^{0.04}\times \\
% & \times\left(\frac{100 x_7}{\cos(x_4)}\right)^{-0.3} (x_8 x_9)^{0.49} + x_1 x_10
%\end{align*}
%\begin{tabular}{|l|l|}
%\hline
%$x_1\in[150, 200]$ & wing area (ft$^2$) \\
%$x_2\in[220, 300]$ & weight of fuel in the wing (lb) \\
%$x_3\in[6, 10]$ & aspect ratio \\
%$x_4\in[-10, 10]$ & quarter-chord sweep (degrees) \\
%$x_5\in[16, 45]$ & dynamic pressure at cruise (lb/ft$^2$) \\
%$x_6\in[0.5, 1]$ & taper ratio \\
%$x_7\in[0.08, 0.18]$ & aerofoil thickness to chord ratio \\
%$x_8\in[2.5, 6]$ & ultimate load factor \\
%$x_9\in[1700, 2500]$ & flight design gross weight (lb) \\
%$x_{10}\in[0.025, 0.08]$ & paint weight (lb/ft$^2$) \\
%\hline
%\end{tabular}

%\subsection{Real case model}
%As a real case example, we will study the payoff function of an arithmetic mean Asian call option. For a discretized Brownian motion $\vect{B}=(B_{t_1}, B_{t_2},\dots, B_{t_d})$ at times $t_i=T\times i/d$, the payoff of the option is:

>>>>

\newcommand{\comment}[1]{{\color{cyan} #1 }}
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

{\color{purple} (Lolo) 
\begin{definition}
\label{rep.designs}
Let $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\mathcal{P}'=\{{\vx'}_i\}_{i=0}^{n-1}$ be two point sets in $[0,1]^{d}$. In these sets, all points $\vx_i$ (resp. $\vx'_i$) are coordinate-wise different, i.e. for all $(i_1,i_2) \in \{0,\dots,n-1\}^2$ such that $i_1 \neq i_2$: $$x_{i_1,j} \neq x_{i_2,j}, \qquad \text{for any  } j=1,\dots,d .$$
Let $\mathcal{P}^u=\{\vx_{i,u}\}_{i=0}^{n-1}$ (resp. ${\mathcal{P}'}^u$), $u \subsetneq \mathcal{D}$, denote the subset of dimensions of $\mathcal{P}$ (resp. $\mathcal{P}'$) indexed by $u$. We say that $\mathcal{P}$ and $\mathcal{P}'$ are two replicated designs of order $a \in \{1,\dots,d-1\}$ if for any $u \subsetneq \mathcal{D}$ such that $|u|=a$, $\mathcal{P}^u$ and ${\mathcal{P}'}^u$ are the same point set in $[0,1]^a$. We define by $\pi_u$ the permutation that rearranges the rows of ${\mathcal{P}'}^u$ into $\mathcal{P}^u$ and exclude the trivial case $\vx_i = \vx'_i$ for all $i\in\{0,\dots,n-1\}$.
\end{definition}
}

@@

\comment{For this article, we assumed that evaluating the model is expensive. Hence, to study the cost we will focus on the number of function evaluations needed to estimate the indices. The function values used to estimate the indices are also used to compute the discrete Walsh coefficients. Thus, there are no additional evaluations needed to compute the error bound. The only computation cost that could be expensive is the fast Walsh transform. However, on a regular laptop, if we consider an extreme case of obtaining $2^{20}$ model values ($\approx$ one million points):
\begin{itemize}
\item At an average evaluation time of $1$ microsecond per point, the total evaluation time is about $1$ second.
\item The fast transform on these values takes around $0.5$ seconds.
\end{itemize}
}

@@

Then, one must construct the two designs $\mathcal{P}_{m}=\{\vx_i\}_{i=0}^{2^{m}-1}$ and $\mathcal{P}'_{m}=\{\vx'_i\}_{i=0}^{2^{m}-1}$ at Step $5$ according to the multiplicative approach detailed in \cite{GJAHMP}. {\color{purple} (Lolo) This approach iteratively constructs a $2d$-dimensional Sobol' sequence then assigns its first $d$ coordinates to $\mathcal{P}_{m}$ and its last $d$ coordinates to $\mathcal{P}'_{m}$. The $2d$-dimensional Sobol' sequence is generated based on the direction numbers found in \cite{Kuo}. These direction numbers optimize the two-dimensional projections of the Sobol' sequence. Although this is the authors choice, one may choose any other Sobol' construction of $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ as long as the $2d$ dimensions are each generated with different primitive polynomials. In addition, $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ are also independently scrambled using Owen's scrambling scheme \cite{HonHic00a,Owe95}.}

@@

We illustrate our sequential estimation procedure with two classical test functions and one academic example. In each case, Sobol' indices are estimated with the following three variants:
\begin{itemize}
\item[$\bullet$] Variant $A.a$ as Variant $A$ without using ``Correlation 2''. 
\item[$\bullet$] Variant $A.b$ as Variant $A$ using ``Correlation 2''.
\item[$\bullet$] Variant $B$.
\end{itemize}
The threshold to decide whether or not a first-order index is small is set to $0.1$.

@@

%\comment{As an academic case example, we will study the wing weight function:
%\begin{align*}
%f(\vx)=0.036 x_1^{0.758} & x_2^{0.0035} \left(\frac{x_3}{\cos(x_4)^2}\right)^{0.6} x_5^{0.006} x_6^{0.04}\times \\
% & \times\left(\frac{100 x_7}{\cos(x_4)}\right)^{-0.3} (x_8 x_9)^{0.49} + x_1 x_10
%\end{align*}
%\begin{tabular}{|l|l|}
%\hline
%$x_1\in[150, 200]$ & wing area (ft$^2$) \\
%$x_2\in[220, 300]$ & weight of fuel in the wing (lb) \\
%$x_3\in[6, 10]$ & aspect ratio \\
%$x_4\in[-10, 10]$ & quarter-chord sweep (degrees) \\
%$x_5\in[16, 45]$ & dynamic pressure at cruise (lb/ft$^2$) \\
%$x_6\in[0.5, 1]$ & taper ratio \\
%$x_7\in[0.08, 0.18]$ & aerofoil thickness to chord ratio \\
%$x_8\in[2.5, 6]$ & ultimate load factor \\
%$x_9\in[1700, 2500]$ & flight design gross weight (lb) \\
%$x_{10}\in[0.025, 0.08]$ & paint weight (lb/ft$^2$) \\
%\hline
%\end{tabular}

%\subsection{Wing weight model}
%As an academic case example, we will study the payoff function of an arithmetic mean Asian call option. For a discretized Brownian motion $\vect{B}=(B_{t_1}, B_{t_2},\dots, B_{t_d})$ at times $t_i=T\times i/d$, the payoff of the option is:

### 2017-02-20 article_review/reviewer_letter.tex
More changes for the review

\textcolor{blue}{Dear associated editor and reviewers,\\
we would like to thank you for the positive and constructive feedback. Below we have
compiled a detailed list of answers (blue text) to the issues raised in the review reports. In particular, in light of reviewer's two remark, the Asian option problem was deleted and replaced with a new ``real function''.\\
Best regards,\\
Laurent Gilquin and Llu\'{i}s Antoni Jim\'{e}nez Rugama}

@@

\begin{itemize}
\item[1.] Page 4, left, line 52: What are $\kappa$ and $\vk(\kappa)$ there? They seem undefined, and then many readers will not understand what follows.
\item[2.] Page 4, right, line 30: Remove the period before (13).
\item[3.] Page 4, right, lines 38--42: We find $\epsilon_{\hat I}$ in (14) and $\epsilon_{I}$ below (seems inconsistent).
\item[4.] Section 5.2: These empirical results are for what parameters $d$, $T$, $S_0$, $\sigma$, $\rho$, $K$? I expect the behavior to depend strongly on the values of these parameters. E.g., large $d$ vs small $d$, large $T$ vs small $T$, large $\sigma$ vs small $\sigma$, etc. Also, this example is largely academic and not based on real-life data; I would not call it a "real-life" example. 
\item[5.] The given examples are only in small dimensions. What about higher-dimensional "real-life" examples?-- Pierre L'Ecuyer
\end{itemize}

@@

@@

\answer{The function values used to estimate the Sobol' indices are the same to compute the discrite Walsh coefficients. Thus, there are no additional function evaluations needed to compute $\widetilde{S}_{l,m}$. }

@@

\answer{As the reviewer claims, this is a key point that we revised and explained with more detail. It is really hard to verify whether an integrand satisfies the cone condition. Indeed, because we choose our mapping $\tilde{\vk}$ heuristically, the cone conditions will also depend on the scrambling. At the end of section 3 we cited some data-based necessary conditions that can help identify when integrands are not in the cone. In addition, also at the beginning of section 5, we note that if the error bound is not satisfied it is certain that the integrand is not in the cone.}
\end{itemize}

@@

\answer{While the RHS holds for any $\ell_*\leq\ell\leq m$, it is definitely not clear how to proceed with the information given in the article. We added more detailed information explaining that one only needs to fix $r=m-\ell$. Once $r$ is chosen, the RHS only depends on $m$.}

@@

{\color{blue} The paragraph has been reworked. The reviewer guessed right. We use a 2d-dimensional Sobol' sequence and assign its first d dimensions to the first design and the remaining ones to the second design. Then, each Sobol' sequence is scrambled independently; except in Variant B where the scrambling is the same to insure that the two designs are replicated designs of order one.

As for the properties of the Sobol' sequences, the ones used in this paper are generated with the directional numbers found by S. Joe and F. Y. Kuo (2008). These directional numbers insure better two-dimensional projections of the resulting Sobol' sequences.}

@@

\answer{As pointed out by the reviewer, some clarification was needed in this paragraph. We added the missing explanation indicating that we replace Owen's iid uniform points by a Sobol' sequence.}

@@

{\color{blue} The ``real case model'' has been replaced with a new one as suggested by the second reviewer. Nonetheless, we thank the reviewer for these corrections that we agreed with.} 
\end{itemize}

@@

{\color{blue} We thank the reviewer for this remark. The definition was intended for point sets where all points are coordinate-wise different. More precisely, consider a point set $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and two points $\vx_{i_1}$, $\vx_{i_2}$, $i_1 \neq i_2$. Then $\vx_{i_1}$ and $\vx_{i_2}$ are coordinate-wise different if: 
$$ x_{i_1,j} \neq x_{i_2,j}, \qquad \forall j=1,\dots,d .$$
Definition 1 has been reworked to include this property. This also tackles the issue of having more than one permutation that would rearrange the rows $\vx'_i$ into $\vx_i$. Now, the permutation is unique.

@@

\answer{More details have been provided in Section 3.1 to help readers follow the ideas behind the approach. Among all additions, $k_{j\ell}$ has been defined and the sums $S_m$, $\hS_{\ell,m}$, $\wcS_m$, $\tS_{\ell,m}$ have been briefly described in conjunction with the cone conditions.}

@@

\answer{
As proposed in this point, we added more information that might be useful for this issue.

@@

{\color {blue} We acknowledge that analytical formulas of Sobol' indices are invariant by adding a constant shift $c$ to the function $f$. As underlined by the reviewer, in our algorithm the addition of a constant shift $c$ modifies the error bound for $\vI_3$ but also the errors bounds for the others integrands ($\vI_1$, $\vI_2$ and $\vI_4$). More generally, our algorithm depends on the analytical expression of the Sobol' index estimator considered.

However, that is not a concern since error bounds for any estimator can be calculated. That is, our algorithm can be adapted to any Sobol' index estimator. In particular, this is done when ``Correlation 2'' is used in Variant A.b instead of (5). Our goal was to design an automatic algorithm that does not ac...}

@@

{\color{blue} We agree with the reviewer that the effective dimension of the higher dimensions integrand might be lower than its lower dimensions counterpart. However, evaluating the effective dimension of each integrands already requires a large number of model evaluations (\textit{c.f.} Wang. X and Fang. K.-T., 2003).

@@

{\color{blue} The Sobol' g-function has been modified according to the reviewer remark. There were no drastic changes observed, perhaps since the scrambling might remove most of the anchoring. Indeed, the new results show that failure rates have improved for all three approaches (Variant A.a, A.b and B).}

@@

{\color{blue} The Asian option problem has been replaced by the wing weight test function taken from the suggested database. Section $5.2$ has been reworked to introduce this new test function. Our results are compared to formers obtained by screening approaches (Moon, H. (2010)).}

@@

{\color{blue} We understand and agree with the issue raised by the reviewer. A possible solution is to choose a less conservative precision $\epsilon$ when dealing with time-expensive functions. In the proposed examples, $\epsilon$ was intentionally fixed small to push forward the performance of our algorithm. That shows the difference in function evaluations cost ....

On another hand, if one has to deal with a function where one day is required to obtain one evaluation, perhaps the use of a screening method is more adequate (less accurate but less greedy). Or if available, one could make use of a cluster to perform multiple model evaluations in parallel.}
\end{itemize}

>>>>

\textcolor{blue}{Dear associated editor and reviewers,\\
we would like to thank you for the positive and constructive feedback. Below we have compiled a detailed list of answers (blue text) to the issues raised in the review reports. In particular, in light of reviewer's two remark, the Asian option problem was replaced with a new ``real function''.\\
Best regards,\\
Laurent Gilquin and Llu\'{i}s Antoni Jim\'{e}nez Rugama}

@@

\begin{itemize}
\item[1.] Page 4, left, line 52: What are $\kappa$ and $\vk(\kappa)$ there? They seem undefined, and then many readers will not understand what follows.

{\color{blue} The notations $\kappa$ and $\tilde{\vk}(\kappa)$ (former $\vk(\kappa)$) are now properly defined.}
\item[2.] Page 4, right, line 30: Remove the period before (13).

{\color{blue} The typo has been fixed.}
\item[3.] Page 4, right, lines 38--42: We find $\epsilon_{\hat I}$ in (14) and $\epsilon_{I}$ below (seems inconsistent).

{\color{blue} The typo has been fixed.}
\item[4.] Section 5.2: These empirical results are for what parameters $d$, $T$, $S_0$, $\sigma$, $\rho$, $K$? I expect the behavior to depend strongly on the values of these parameters. E.g., large $d$ vs small $d$, large $T$ vs small $T$, large $\sigma$ vs small $\sigma$, etc. Also, this example is largely academic and not based on real-life data; I would not call it a "real-life" example.

{\color{blue} The ``real case model'' has been replaced with another academic application as suggested by the second reviewer. Nonetheless, we thank the associate editor for pointing out these corrections.}
\item[5.] The given examples are only in small dimensions. What about higher-dimensional "real-life" examples?-- Pierre L'Ecuyer

{\color{blue} The new academic application is in dimension $10$. For higher-dimensional examples, we expect the effective dimension to be much smaller than its nominal dimension. Otherwise, a high dimensional problem with high effective dimension will be hard to deal with in most applications. In low effective dimensional problems, most Sobol' indices will have a small value. As shown in the examples, all the small value indices are very easily estimated. Furthermore, the estimator ``Correlation 2'' can (in some cases) reduce further the function values needed for inputs with small main effects.}
\end{itemize}

@@

{\color{blue} The points raised in this remark are crucial. We expect to have answered these questions with the information added the article.

Below we address the remark: ``simpler methods based on random sampling and straightforward confidence intervals become more attractive, as they have no extra cost and potentially a better assessment of how likely it is that the error is met''.

The cost of constructing the error bound is a computational cost and not a numerical cost. That is, it does not require extra model evaluations. This point is further discussed in question 2.

For the estimation of the integrands, random sampling methods have convergence rates of $\mathcal{O}(n^{-1/2})$ instead of the quasi-Monte Carlo methods $\mathcal{O}(n^{-1+\delta})$. Hence, we expect the precision of our procedure to be better than those of random sampling methods that use confidence intervals (asymptotic or bootstrap based). In our approach, the construction of the error bounds is analytical even if the Sobol' sequence is randomly sampled. However, in other random sampling methods the confidence intervals are estimated entirely from the sampling points and are less accurate.

To confirm this claim, the precision of our procedure is compared to bootstrap confidence intervals obtained from random sampling. The comparison is carried out for the Bratley test function in Section 5.3. Results show that for an equivalent number of evaluations, random methods using confidence intervals are less accurate than our procedure.}

@@

\answer{We added an explanation at the beginning of Section 4. The function values used to estimate the Sobol' indices are the same ones used to compute the discrete Walsh coefficients. Thus, there are no additional function evaluations needed to compute $\widetilde{S}_{\ell,m}$. The only cost we should consider is the computational cost of calculating the fast transform. However, on a regular laptop, in the extreme case of $2^{20}$ model evaluations, the fast transform takes around $0.5$ seconds.}

@@

\answer{As the reviewer claims, this is a key point that we revised and explained with more detail. It is really hard to verify whether an integrand satisfies the cone condition. Indeed, because we choose our mapping $\tilde{\vk}$ heuristically, the cone conditions will also depend on the scrambling. At the end of section 3 we cited some data-based necessary conditions that can help identify when integrands are not in the cone. In addition, also at the beginning of section 5, we noted that if the error bound is not satisfied it is certain that the integrand is not in the cone.}
\end{itemize}

@@

\answer{While the RHS holds for any $\ell_*\leq\ell\leq m$, it is definitely not clear how to proceed with the information given in the article. We added more details clarifying that one only needs to fix $r=m-\ell$. Once $r$ is chosen, the RHS only depends on $m$.}

@@

{\color{blue} The paragraph has been reworked. The reviewer guessed right. We use a 2d-dimensional Sobol' sequence and assign its first d dimensions to the first design and the remaining ones to the second design. Although this is our choice, one may choose any other Sobol' construction of $\mathcal{P}_{m}$ and $\mathcal{P}'_{m}$ as long as the $2d$ dimensions are each generated with different primitive polynomials. After that, each Sobol' sequence is scrambled independently; except in Variant B where the scrambling of both designs should be the same to ensure that both designs after the scrambling are replicated of order one.

As for the properties, in this paper we generate the sequences with the direction numbers found by S. Joe and F. Y. Kuo (2008) who optimized the two-dimensional projections.}

@@

\answer{As pointed out by the reviewer, some clarification was needed in this paragraph. We indicated that we extend the use of  Owen's estimator by using Sobol' sequences instead of iid random points.}

@@

{\color{blue} The ``real case model'' has been replaced with a new one suggested by the second reviewer. Nonetheless, we thank the reviewer for these corrections that we agreed with.} 
\end{itemize}

@@

{\color{blue} We thank the reviewer for this remark. Definition 1 is not intended to describe good points. It simply generalizes the definition of replicated designs to suggest the use of a bigger set of types of points. For instance, this definition clearly includes orthogonal arrays and Sobol' sequences, but rank-1 lattices are another type of points that could also generate replicated designs of order 1. Each of them are different types of points whose quality is measured with different tools. The authors think that at this point, the quality should be studied by type of points instead.

Nonetheless, we modified the definition to only consider point sets whose points are coordinate-wise different. More precisely, consider $\mathcal{P}=\{\vx_i\}_{i=0}^{n-1}$ and $\vx_{i_1}$, $\vx_{i_2}$, two different points from this set. Then $\vx_{i_1}$ and $\vx_{i_2}$ are coordinate-wise different if: 
$$ x_{i_1,j} \neq x_{i_2,j}, \qquad \forall j=1,\dots,d .$$
Definition 1 has been reworked to include this property. This solves the issue of having more than one permutation that would rearrange the rows $\vx'_i$ into $\vx_i$. Now, the permutation is unique.

@@

\answer{More details have been provided in Section 3.1. Among all additions, $k_{j\ell}$ has been defined and the sums $S_m$, $\hS_{\ell,m}$, $\wcS_m$, $\tS_{\ell,m}$ have been briefly described in conjunction with the cone conditions.}

@@

\answer{
As proposed in this remark, we added more information at the end of Section 3 to clarify the issue.

@@

{\color {blue} We acknowledge that analytical formulas of Sobol' indices are invariant by adding a constant shift $c$ to the function $f$. As underlined by the reviewer, in our algorithm the addition of a constant shift $c$ modifies the error bound for $\vI_3$ but also the error bounds for the integrands $\vI_1$ and $\vI_2$.

However, our goal is to design an automatic (finds the number of points needed automatically) and adaptive (adapts to the difficulty of the problem) algorithm whose inputs are only:
\begin{itemize}
\item the absolute error tolerance.
\item the black-box $f$ that only gives the value of $f(\vx)$ at any $\vx\in [0,1]^d$.
\end{itemize}
Without additional information and for the class of functions defined, the algorithm cannot distinguish whether a finite number of function values correspond to a shifted model or to another completely different model. We could restrict to a smaller class of functions to modify the algorithm and detect the shift case, but we preferred providing a more general algorithm.}

@@

{\color{blue} We agree with the reviewer that the effective dimension of the $2d-1$ integrand might be lower than the $d+1$ integrand. However, estimating the effective dimension of each integrand already requires a large number of model evaluations (\textit{c.f.} Wang. X and Fang. K.-T., 2003).

@@

{\color{blue} The Sobol' g-function has been modified according to the reviewer's remark. There were no drastic changes observed, perhaps because the scrambling removes the anchoring. Indeed, the new results show that failure rates have improved for all three approaches (Variant A.a, A.b and B).}

@@

{\color{blue} The Asian option problem has been replaced by the wing weight test function taken from the suggested database. Section $5.2$ has been reworked to introduce this new test function. Our results are compared to older results obtained by screening approaches (Moon, H. (2010)).}

@@

{\color{blue} We understand and agree with the issue raised by the reviewer. A possible solution is to choose a less conservative precision $\epsilon$ when dealing with time-expensive functions. The algorithm also allows to modify the maximum number of points allowed to estimate the indices. In the proposed examples, $\epsilon$ was intentionally fixed small to push forward the performance of our algorithm. That clearly shows the difference in number of function evaluations needed to estimate different indices for the same model.

If one has to deal with a function where one day is required to obtain one evaluation, perhaps the use of a screening method is more adequate (less accurate but less greedy). Or if available, one could make use of a cluster to perform multiple model evaluations in parallel.}
\end{itemize}
